On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-02 tt_intro.tex
Binding capability
The definition of bc was not correct so that I fixed it.

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \draw (0:0) circle [radius=0.05];
      \draw (0:1) circle [radius=0.05];
      \draw (180:1) circle [radius=0.05];
      \node[above] at (0:1) { $p^\prime$ };
      \node[above] at (0:0) { $p$ };
      \node[above] at (180:1) { $p^\prime$ };

@@

        \fill (60 : 1) circle [radius=0.1];
        \fill (-60 : 1) circle [radius=0.1];
        \fill (120 : 1) circle [radius=0.1];
        \fill (-120 : 1) circle [radius=0.1];
        \node[above] at (60 :1) { $a_{j_1}$ };
        \node[above] at (-60 :1) { $a_{j_2}$ };
        \node[above] at (120 :1) { $a_{j_3}$ };
        \node[above] at (-120 :1) { $a_{j_4}$ };
      \end{scope}
    \end{tikzpicture} 
    \caption{Through a tunnel section}
    \label{TTT_tunnel_intro}
  \end{center}
\end{figure}

@@

At delay 1, a bead cannot collaborate with its successors in order to stabilize itself. 
In fact, there are just two ways for a bead to get stabilized at delay 1 (or the bead has no place to be stabilized around so that the system halts). 
One is to be bound and the other is through a 1-in-1-out structure called the tunnel section. 
See Fig.~\ref{fig:TTT_tunnel}. 
A \textit{tunnel section} consists of four beads that occupy four neighbors of one free point. 
The behavior of a deterministic oritatami system at delay 1 can be described by a sequence of $S$ of $b$ (bound), $t_s$ (straight tunnel section), $t_o$ (obtuse-turn tunnel section), and $t_a$ (acute-turn tunnel section); priority is given to tunnel, that is, $S[i]$ is $t_s$ (resp.~$t_o$, $t_a$) if the $i$-th bead of the system is stabilized not only by being bonded but also through a straight (resp. obtuse-turn, acute-turn) tunnel section. 
We let $S$ take the value $\blacksquare$ for halt (due to the lack of free neighbors).

Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free. We call such a point $p$ the $inside\ of\ a\ tunnel$ and points $p^\prime$ the $entrance\ of\ a\ tunnel$ except when $p^\prime$ is inside of a tunnel. If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor. In this way, $w[i]$ can get stabilized without being bound.

@@

We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$. 
Taking this reachability into account, we define the \textit{binding capability} of a conformation as the number of free bonds of its beads available geometrically for elongations of $C$.
It is defined formally as follows:

\begin{definition}[binding capability]
Let $C = (P,w,H)$ be a conformation.
Let $B_k$ be $H \cap \{ (i,j) \mid \mbox{$i=k$ or $j=k$} \}$. Moreover, let $R_k$ be a set of neighbors of the point $P[k]$ that are free and reachable from $C$.
 The binding capability of $C$, denoted by $\#bc(C)$, is defined by $\sum^{|w|}_{k=1} \min \{ |B_k|, |R_k|  \}$.
\end{definition}

>>>>

\begin{comment}
\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \draw (0:0) circle [radius=0.05];
      \draw (0:1) circle [radius=0.05];
      \draw (180:1) circle [radius=0.05];
      \node[above] at (0:1) { $p^\prime$ };
      \node[above] at (0:0) { $p$ };
      \node[above] at (180:1) { $p^\prime$ };

@@

        \fill (60 : 1) circle [radius=0.1];
        \fill (-60 : 1) circle [radius=0.1];
        \fill (120 : 1) circle [radius=0.1];
        \fill (-120 : 1) circle [radius=0.1];
        \node[above] at (60 :1) { $a_{j_1}$ };
        \node[above] at (-60 :1) { $a_{j_2}$ };
        \node[above] at (120 :1) { $a_{j_3}$ };
        \node[above] at (-120 :1) { $a_{j_4}$ };
      \end{scope}
    \end{tikzpicture} 
    \caption{Through a tunnel section}
    \label{TTT_tunnel_intro}
  \end{center}
\end{figure}
\end{comment}

@@

At delay 1, a bead cannot collaborate with its successors in order to stabilize itself. 
In fact, there are just two ways for a bead to get stabilized at delay 1 (or the bead has no place to be stabilized around so that the system halts), as observed in \cite{DHOPRSST2018}. 
One is to be bound and the other is through a 1-in-1-out structure called the tunnel section. 
See Fig.~\ref{fig:TTT_tunnel}. 
A \textit{tunnel section} consists of four beads that occupy four neighbors of one free point. 
In order for an oritatam system to stabilize the bead $w[i]$ at the central point $p$ of a tunnel section, its predecessor $w[i-1]$ must be put at one of the two free neighbors of $p$. 
Thus, at the stabilization of $w[i]$, only one neighbor of $p$ is left free so that the successor $w[i+1]$ is to be stabilized there, even without being bound. 
In this case, the point where $w[i-1]$ is stabilized is considered to be an \textit{entrance of the tunnel} and the point where $w[i+1]$ is stabilized is considered as an \textit{exit of the tunnel}.

The behavior of an oritatami system at delay 1 can be described by a sequence of $S$ of $b$ (bound), $t_s$ (straight tunnel section), $t_o$ (obtuse-turn tunnel section), and $t_a$ (acute-turn tunnel section); priority is given to tunnel, that is, $S[i]$ is $t_s$ (resp.~$t_o$, $t_a$) if the $i$-th bead of the system is stabilized not only by being bonded but also through a straight (resp. obtuse-turn, acute-turn) tunnel section. 
We let $S$ take the value $\blacksquare$ for halt (due to the lack of free neighbors).

%Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free. We call such a point $p$ the $inside\ of\ a\ tunnel$ and points $p^\prime$ the $entrance\ of\ a\ tunnel$ except when $p^\prime$ is inside of a tunnel. If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor. In this way, $w[i]$ can get stabilized without being bound.

@@

%We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$. 
We say that a neighbor of a point $p$ is reachable from a conformation $C$ if there exists an elongation of $C$ in which a bead occupies the neighbor and it binds with a bead at $p$. 
Taking this reachability into account, we define the \textit{binding capability} of a conformation as the number of free bonds of its beads available geometrically for elongations of $C$.
It is defined formally as follows:

\begin{definition}[Binding Capability]
Let $\alpha$ be an arity and $C = (P,w,H)$ be a conformation of arity at most $\alpha$.
Let $H_k = H \cap \{ (i,j) \mid \mbox{$i=k$ or $j=k$} \}$. 
Moreover, let $R_k$ be a set of neighbors of the point $P[k]$ that are free and reachable from $C$.
The binding capability of $C$ at arity $\alpha$, denoted by $\#bc_\alpha(C)$, is defined by $\sum^{|w|}_{k=1} \min \{\alpha-|H_k|, |R_k|\}$.
Whenever the arity is clear from context, we omit the subscript $\alpha$. 
\end{definition}
